SIR Model With Testing Flows and Isolation

### 2020-12-01 codes/ali_test_sir.Rmd
bmb notes

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
    # theme(panel.spacing=grid::unit(0,"lines")) # initial theme, comment it for TTI testing plot
    theme(panel.spacing=grid::unit(0,"lines"),legend.position = "none") #AG, uncomment for Random Case
# p1_temp <- (p1
#     + geom_contour_filled(breaks=pretty(unique(df2$R0_sub),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=1,alpha=0.5,colour="black")
#     + facet_grid(eta_w~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="R[0]"))
#     + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
#     + geom_rect(data=df2,
#                           fill=ifelse(df2$eta_c>df2$eta_w,"white","NA" ),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)
#     )

p1_temp <- (p1
    + geom_contour_filled(breaks=seq(0.80,1.05,by=0.05)
                          )
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
    + geom_rect(data=df2,
                          fill=ifelse(df2$eta_c>df2$eta_w,"white","NA" ),
                          color= NA,
                          ymin=-1,
                          ymax=10,
                          xmin=-1,
                          xmax=2)
    )
p1_temp
# ## hack (By Dr. Ben Bolker) white rectangle to cover grid
#   ggplot() + 
#   scale_x_continuous(name="x") + 
#   scale_y_continuous(name="y") +
#   facet_grid(eta_w~eta_c, labeller=label_special) +
#     geom_rect(data=df2_fake,
#                           fill=ifelse(df2_fake$eta_c>df2_fake$eta_w,"white","black"),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)

@@

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
p2_temp <- (p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"))
    + ggtitle("W[S]=1, W[I]=W[R]=1")
)
p2_temp
# ggsave(p2_temp,filename = "R0contour_random_s.png" , path="../pix/")
```

>>>>

**TO DO** (for contour plots):

- save as PDF
- separate code for these plots into a separate .R file that can be run with a single batch command
- consider using `tikzDevice`

@@

```{r show_contours_1, width=24,height=24,message=FALSE,warning=FALSE}
brks_vec <- seq(0.8,1.05,by=0.05)
p1 <- ggplot(df2,aes(x=omega,y=rho,z=R0_sub))+ theme_bw() +
  xlab(TeX('$\\omega$, Returning test result rate (1/day)')) +
  ylab(TeX('$\\rho$, testing intensity (1/day per capita)')) +
    # theme(panel.spacing=grid::unit(0,"lines")) # initial theme, comment it for TTI testing plot
    theme(panel.spacing=grid::unit(0,"lines"),legend.position = "none") #AG, uncomment for Random Case
# p1_temp <- (p1
#     + geom_contour_filled(breaks=pretty(unique(df2$R0_sub),5),
#                           alpha=0.5) ## breaks=0.2)
#     + geom_contour(breaks=1,alpha=0.5,colour="black")
#     + facet_grid(eta_w~eta_c, labeller=label_special)
#     + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
#     + scale_fill_viridis_d(name=parse(text="R[0]"))
#     + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
#     + geom_rect(data=df2,
#                           fill=ifelse(df2$eta_c>df2$eta_w,"white","NA" ),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)
#     )

p1_temp <- (p1
    + geom_contour_filled(breaks=brks_vec)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(eta_w~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"), breaks=brks_vec)
    + ggtitle(TeX(sprintf("W_S=%.1f, W_I=W_R=1",W_S)))
    + geom_rect(data=df2,
                          fill=ifelse(df2$eta_c>df2$eta_w,"white","NA" ),
                          color= NA,
                          ymin=-1,
                          ymax=10,
                          xmin=-1,
                          xmax=2)
    )
p1_temp
# ## hack (By Dr. Ben Bolker) white rectangle to cover grid
#   ggplot() + 
#   scale_x_continuous(name="x") + 
#   scale_y_continuous(name="y") +
#   facet_grid(eta_w~eta_c, labeller=label_special) +
#     geom_rect(data=df2_fake,
#                           fill=ifelse(df2_fake$eta_c>df2_fake$eta_w,"white","black"),
#                           color= NA,
#                           ymin=-1,
#                           ymax=10,
#                           xmin=-1,
#                           xmax=2)

@@

```{r show_contours_2, width=24,height=24,message=FALSE,warning=FALSE}
p11 <- ggplot(df22,aes(x=omega,y=rho,z=R0))+ theme_bw() +
    theme(panel.spacing=grid::unit(0,"lines"))
p2_temp <- (p11
    + geom_contour_filled(breaks=pretty(unique(df22$R0),5),
                          alpha=0.5) ## breaks=0.2)
    + geom_contour(breaks=1,alpha=0.5,colour="black")
    + facet_grid(s~eta_c, labeller=label_special)
    + scale_x_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_y_continuous(expand=expansion(c(0,0)), n.breaks=3)
    + scale_fill_viridis_d(name=parse(text="R[0]"),breaks=brks_vec)
    + ggtitle("W[S]=1, W[I]=W[R]=1")
)
p2_temp
## ggsave(p2_temp,filename = "R0contour_random_s.png" , path="../pix/")
ggsave(p2_temp,filename = "R0contour_random_s.pdf" , path="../pix/")
```
